---
title: "An Example Run for MoMPCA"
author: "Anonymous Author(s)"
date: "11 February 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load the libraries required and load the file, "functions.R", which contains the MoMPCA frunction.
```{r}
library(RSpectra)
library(pracma)
source('function.R')
```
Load the data as follows. 
```{r}
X=read.csv('motivating_example.csv')
X=data.matrix(X)
```
Run the MoMPCA function to find the first principal component. We take $L=25$.
```{r}
l=MoMPCA(X,L=25,d=1,eta=0.0001,tmax=100,verbose=1)
```
We plot the scatter plot of the data along the PC1 for MoMPCA (colored in blue) and classical PCA (colored in red) in Figure 1. Even in the presence of only 1% outlying observations, the classical PCA can render spurious results while MoM PCA finds the direction of maximum variation efficiently.
```{r, echo=FALSE}
S=t(X)%*%X
res=eigen(S)
V1=res$vectors[,1]
plot(X,xlab='Feature 1', ylab='Feature 2', main='Figure 1: MoMPCA vs. Classical PCA')
abline(0,l$V[2]/l$V[1],col='blue')
abline(0,V1[2]/V1[1],col='red')
```
 
 